Logarithmic Space Verifiers on NP-complete

### 2019-11-15 doc/manuscript.tex
Fixed the content proof

On the one hand, every language in $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$. The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right. Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$. Hence, we obtain that $L \subseteq 2L$. Since we already know that $2L \subseteq L$, then $L = 2L$.

On the other hand, every language in $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is also simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.

As result, $L = NL$ if and only if $2L = 2NL$. We define the class $LNL$ as the languages
\[L''' =\{yz: y \in L' \textit{ and } z \in L'' \textit{ such that } L' \in L \textit{ and } L'' \in NL\}.\]
Therefore, we can deterministic logarithmic space reduce every language $L''' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language in $L_{2} \in 1L$ when $L = NL$. In this way, we can make a relation between every language $L_{1} \in 1LNL$ to a language $L_{2} \in 1L$. We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1LNL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
\[L_{2, i} = \{i \sqcup j: j \in L_{2}\}\]
and $\sqcup$ is the blank symbol \cite{Pap03}. We can make this because $1LNL$ is enumerable due to $P$ is also enumerable and $1LNL \subseteq P$ \cite{Pap03}. However, we know for every natural number $i$ that $L_{2, i}$ belongs to $1L$, since $L_{2} \in 1L$ and we can check in a deterministic one-way computation the nonempty prefix substring $i$ without using any amount of space in the work tapes. Hence, we obtain that $|1LNL|_{c} < |1L|_{c}$ using this modified relation which is bijective, because there are languages in $1L$ such that the instances do not contain the blank symbol. However, this is not possible according to the Theorem \ref{partially}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

>>>>

On the one hand, every language $L' \in L$ which is decided by a deterministic logarithmic space Turing machine $M$ could be $\textit{L--reduced}$ to a language in $1L$. The reason is simple, because the Turing machine $M$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $M$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a deterministic one-way logarithmic space Turing machine, that would be the same Turing machine $M$ where this one will always read on the input tape from left-to-right. Certainly, when $M$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $M$ in case of acceptance will output the strings that consist in a language in $1L$. Hence, we obtain that $L \subseteq 2L$. Since we already know that $2L \subseteq L$, then $L = 2L$.

On the other hand, every language $L'' \in NL$ which is decided by a nondeterministic logarithmic space Turing machine $N$ could be $\textit{NL--reduced}$ to a language in $1NL$. The reason is also simple, because the Turing machine $N$ could output the sequence of symbols that is read consecutively in the input tape during the whole computation in case of acceptance. Indeed, for every read symbol in the input tape in $N$, then this is written to the output tape in a sequential way. In this way, the output string could be accepted by a nondeterministic one-way logarithmic space Turing machine, that would be the same Turing machine $N$ where this one will always read on the input tape from left-to-right. Certainly, when $N$ tries to move the head of the input tape to the left into the output string, then this will move contiguously to the right. Consequently, $N$ in case of acceptance will output the strings that consist in a language in $1NL$. Hence, we obtain that $NL \subseteq 2NL$. Since we already know that $2NL \subseteq NL$, then $NL = 2NL$.

As result, $L = NL$ if and only if $2L = 2NL$. We define the class $LNL$ as the languages
\[L''' =\{yz: y \in L' \textit{ and } z \in L'' \textit{ such that } L' \in L \textit{ and } L'' \in NL\}.\]
Therefore, we can deterministic logarithmic space reduce every language $L''' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language $L_{2} \in 1L$ when $L = NL$. In this way, we can make a relation between every language $L_{1} \in 1LNL$ to a language $L_{2} \in 1L$. We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1LNL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
\[L_{2, i} = \{i \sqcup j: j \in L_{2}\}\]
and $\sqcup$ is the blank symbol \cite{Pap03}. We can make this because $1LNL$ is enumerable due to $P$ is also enumerable and $1LNL \subseteq P$ \cite{Pap03}. However, we know for every natural number $i$ that $L_{2, i}$ belongs to $1L$, since $L_{2} \in 1L$ and we can check in a deterministic one-way computation the nonempty prefix substring $i$ without using any amount of space in the work tapes. Hence, we obtain that $|1LNL|_{c} < |1L|_{c}$ using this modified relation which is bijective, because there are languages in $1L$ such that the instances do not contain the blank symbol. However, this is not possible according to the Theorem \ref{partially}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}
